---
title: "Biodiversity Data Work"
author: "Lucy Wall"
date: "31/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(popbio)
```
```{r}
percent_cover_data <- read.csv("data-entry-final - percent-cover.csv")
biodiversity_data <- read.csv("data-entry-final - biodiversity.csv")
```

#Species richness in each quadrat
- assign each quadrat a substrate type (whichever has highest percent cover)
- counting total number of species found in each quadrat
- box plot with dots, species richness graphed against substrate category 



#Shannon Biodiversity Index in each quadrat
- calculate proportions of species
  - #individuals of a species = (count in square*10) + (count in another square *10) **(DO THIS TO SUM ALL SQUARES THAT HAVE THE SAME SPECIES)
  - total #individuals in quadrat (sum of all #individuals of a species)
  - proportions = #of individuals of a species/ (total #individuals in quadrat)
  
-Shannon Wiener Index
  - H = -SUM(proportion of species * ln(proportion of species))
  
***graph by percent cobble in each quadrat***
  
