---
title: "Biodiversity Sampling - Hannah"
author: "Hannah Levit"
date: "31/10/2021"
output: html_document
---

QUESTION: How does substrate impact biodiveristy? - specifically types of rock - sand, pebble, cobble, boulder, or bedrock

SUMMARY OF DATA USED: We did our sampling at two different parallel transects in Scott's bay. The transects were taken during high tide on mostly pebble, cobble and boulder substratum. 

```{r}

biodiversity = read.csv("data-entry-final - biodiversity.csv")
summary(biodiversity)
view(biodiversity)

percent_cover = read.csv("data-entry-final - percent-cover.csv")
summary(percent_cover)

quadrat_data = read.csv("data-entry-final - quadrat-data.csv")
summary(quadrat_data)

```


POTENTIAL ANALYSIS:
- plot species diversity and substrate type 
n and abiotic_hab

```{r}
library(ggplot2)
library(patchwork)
library(tidyverse)

ordered_biodiversity = biodiversity %>%
  arrange(abiotic_hab)
# find number of species per substrate type
  
# should the pebbles,cobble column be changed?


ordered_biodiversity

ggplot(ordered_biodiversity, aes(x = abiotic_hab, y = n, fill = abiotic_hab)) + 
  geom_boxplot() +
  labs(y = "Number of individuals", x = "Substrate type")

```


SUMMARY OF ANALYSIS TO ANSWER QUESTION:

RESULTS AND CONCLUSIONS WITH GRAPHS AND FIGURES:








SUBMIT: 
1. A file containing your summary and analysis `group-summary.md` that includes:
  a. Your hypothesis or question
  b. Summary of data collection/ types of data used (1-2 sentences)
  c. Summary of the analyses you did to answer your question (1-2 sentences)
  d. Results and conclusions (1-2 sentences) with associated graphs and figures
2. A folder called `images` where you save the images you make to `.png` files for the rest of your group to use. 
  - when you create the plots from your data, you can save the plot using the code `ggsave([plot-name], here("./images/[file-name].png)` where the `[plot-name]` and `[file-name]` are what you have chosen to call your ggplot objects and the file you're writing out. 
3. An `RProject` so your code is completely reproducible
4. A knit pdf version of your `group-summary.md` file 