---
title: "Field Sampling Final Code"
author: "Paige Amos"
date: "31/10/2021"
output: pdf_document
---

QUESTION: How does substrate impact sessile biodiversity in the intertidal? - specifically types of rock - sand, pebble, cobble, boulder, or bedrock

SUMMARY OF DATA USED: We did our sampling at two different parallel transects in Scott's bay. The transects were taken during high tide on mostly pebble, cobble and boulder substratum. 

```{r}
library(tidyverse)
library(here)
```

```{r}
biodiversity = read_csv(here("./data/biodiversity.csv"))
knitr::kable(biodiversity, caption = "Biodiversity of invertebrates on various substrates")

cover = read_csv(here("./data/cover.csv"))
knitr::kable(biodiversity, caption = "Cover data")

quadrat = read_csv(here("./data/quadrat.csv"))
knitr::kable(biodiversity, caption = "Quadrat data")
```

```{r}
merged_data_1 = merge(biodiversity, cover)
head(merged_data_1)

merged_data_1 <- merged_data_1 %>%
  select(-c(biotic_hab, per_mussel, per_barnacle, per_upright, per_crust, num_snail, num_crab))


#number of individuals per species in the 10 squares
quad_shannon <- biodiversity %>%
  drop_na(n) %>%
  group_by (vertical_transect, quadrat, species) %>%
  summarize(n_per_species = sum(n))

#of occurrences per quadrat
quad_occ_count <- biodiversity %>%
  drop_na(species, n) %>%
  group_by(vertical_transect, quadrat, species) %>%
  summarize(occ_count_per_quadrat = n())

#of species per quadrat
quad_species_count <- quad_occ_count %>%
  group_by(vertical_transect, quadrat) %>% 
  summarize(species_per_quad = n())

#total number of individuals of all species in quadrat found in the 10 squares
quad_total <- biodiversity %>%
  drop_na(species, n) %>%
  group_by(vertical_transect, quadrat) %>%
  summarize(n_total_per_quadrat = sum(n))

quad_shannon_2 <- merge(quad_shannon, quad_total, all = TRUE, by = c('vertical_transect', 'quadrat'))

quad_shannon_3 <- quad_shannon_2 %>%
  drop_na(species) %>%
  mutate(p_i = n_per_species/n_total_per_quadrat) %>%
  mutate(Pi_lnPi = p_i*log(p_i))

#calulating shannon wiener for each quadrat and adding to merged data
shannon_index <- quad_shannon_3 %>%
  group_by(vertical_transect, quadrat) %>%
  summarize(H = -sum(Pi_lnPi))

merged_data_2 <- merge(quad_shannon, cover)
merged_data_3 <- merge(merged_data_1, shannon_index)


```

#THIS IS THE FINAL DATASET TO MAKE FIGURES FROM#
```{r}
final_merged_data <- merge(merged_data_3, quad_species_count, all = TRUE, by = c('vertical_transect', 'quadrat')) %>%
  unite(transect_quad, vertical_transect, quadrat)

```

make boxplot of species richness for each substrate type

<<<<<<< HEAD
```{r}
figure_data = final_merged_data %>%
  mutate(transect_quad = as.factor(transect_quad))

species_rich <- ggplot(figure_data, aes(x = per_cobble, y = species_per_quad, fill = transect_quad)) +
  geom_point(aes(colour = transect_quad, size = 2)) +
   stat_smooth(method = "lm", aes(fill = "transect_quad", colour = "black")) +
  xlab("Percent Cobbles (%)") +
  ylab("Species Richness") +
  theme_classic() +
  theme(legend.position = "none")
  
species_rich

```
```{r}
shannon_plot_cobble <- ggplot(figure_data, aes(x = per_cobble, y = H)) +
  geom_point(aes(colour = transect_quad, size = 2)) +
  theme_classic() +
  xlab("Percent Cobbles (%)") +
  ylab("Shannon Wiener Index") +
  stat_smooth(method = "lm", aes(fill = "transect_quad", colour = "black")) +
  theme(legend.position = "none")
  

shannon_plot_cobble
```
```{r}
shannon_plot_pebble <- ggplot(figure_data, aes(x = per_pebble, y = H)) +
  geom_point(aes(colour = transect_quad, size = 2)) +
  theme_classic() +
  xlab("Percent Pebble (%)") +
  ylab("Shannon Wiener Index") +
  stat_smooth(method = "lm", aes(fill = "transect_quad", colour = "black")) +
  theme(legend.position = "none")
  

shannon_plot_pebble
```

SUMMARY OF ANALYSIS TO ANSWER QUESTION:

RESULTS AND CONCLUSIONS WITH GRAPHS AND FIGURES:

